---
title: Covid-19 in Connecticut
subtitle: Data Visualizations
author:
  - David Braze
email: davebraze@gmail.com
institution: FDB Research
date: "`r format(Sys.time(), '%B %d, %Y')`"

# bibliography: ["al-report.bib"]
# biblio-style: "apalike"
# link-citations: true

always_allow_html: false
fontsize: 11pt
geometry: margin=1in
header-includes:
  - \usepackage{booktabs}

output:
  bookdown::tufte_html2:
    keep_md: true
    pandoc_args:
    - --lua-filter
    - "c:/Program Files/R/R-3.6.1/library/rmarkdown/rmd/lua/pagebreak.lua"

  bookdown::html_document2:
    keep_md: true
    theme: cerulean
    number_sections: no
    highlight: tango
    toc: yes
    toc_depth: 2
    toc_float: yes
    pandoc_args:
    - --lua-filter
    - "c:/Program Files/R/R-3.6.1/library/rmarkdown/rmd/lua/pagebreak.lua"
    
  bookdown::pdf_document2:
    keep_tex: true
    highlight: tango
    toc: yes
    number_sections: no
    pandoc_args:
    - --lua-filter
    - "c:/Program Files/R/R-3.6.1/library/rmarkdown/rmd/lua/pagebreak.lua"

---


```{r setup, echo=FALSE, include=FALSE}

## To render this document from a guaranteed clean R environment, use
## the provided Makefile.

## To load all objects referenced in this file into the current R
## environment, make the following call at the R prompt:

knitr::opts_chunk$set(fig.width=7,
                      fig.height=7/(16/9),
                      dpi=200,
                      tinytex.verbose=TRUE, ## PDFs very slow to compile.
                      echo=FALSE,
                      include=FALSE,
                      results='asis',
                      cache=TRUE,
                      warning=FALSE)

## Also see knitr::opts_current$get() within a chunk to inspect then-active options.

options(tinytex.verbose=TRUE,
        tinytex.clean=FALSE)

```

```{r workhorse}

source("./ct-covid.R")

```

# Read This First

```{r readme, include=TRUE}

cat(paste0(readLines("readme.md", n=-1), collapse="\n"))

```

# Introduction to this Page

I started putting together graphs based on Connecticut Department of Public Health (DPH) data in late March, and I've been tweeting some of those graphs since the first week of April. If you're interested in what some of those earlier graphs looked like, you can find them on Twitter at 
[https://twitter.com/search?q=%23Connecticut%20%23covid19%20%40davidbraze&src=typed_query](https://twitter.com/search?q=%23Connecticut%20%23covid19%20%40davidbraze&src=typed_query). 

This page (the one you're looking at now) doesn't have all the graphs I've built. I expect to grow the collection, and add some narrative around the graphs, as time permits. Of course, I'll update the graphs as new data rolls in. Don't expect daily updates, but I guess I'll get around to it at least a couple of times a week. The date at the top of the page will always indicate when it was last updated.

# Show Me the Pictures

## Statewide Summary

```{r ct-stat-daily-change, include=TRUE, fig.height=7}

ct.stat.daily.change.plt

```

```{r usa-state-corona, include=TRUE}

usa.state.corona.plt

```


## Each Town

```{r town-rate, include=TRUE}

town.rate.plt

```

```{r town-by-county-rate, include=TRUE, fig.height=7}

town.by.county.rate.plt

```

```{r map-today, include=TRUE, fig.height=7}

map.today

```
