---
title: Covid-19 in Connecticut
subtitle: Data Visualizations
author:
  - David Braze
email: davebraze@gmail.com
institution: FDB Research
date: "`r format(Sys.time(), '%B %d, %Y')`"

# bibliography: ["al-report.bib"]
# biblio-style: "apalike"
# link-citations: true

always_allow_html: false
fontsize: 11pt
geometry: margin=1in
header-includes:
  - \usepackage{booktabs}

output:
  bookdown::tufte_html2:
    keep_md: true
    pandoc_args:
    - --lua-filter
    - "c:/Program Files/R/R-3.6.1/library/rmarkdown/rmd/lua/pagebreak.lua"

  bookdown::html_document2:
    keep_md: true
    theme: cerulean
    number_sections: no
    highlight: tango
    toc: yes
    toc_depth: 2
    toc_float: yes
    pandoc_args:
    - --lua-filter
    - "c:/Program Files/R/R-3.6.1/library/rmarkdown/rmd/lua/pagebreak.lua"
    
  bookdown::pdf_document2:
    keep_tex: true
    highlight: tango
    toc: yes
    number_sections: no
    pandoc_args:
    - --lua-filter
    - "c:/Program Files/R/R-3.6.1/library/rmarkdown/rmd/lua/pagebreak.lua"

---


```{r setup, echo=FALSE, include=FALSE}

## To render this document from a guaranteed clean R environment, use
## the provided Makefile.

## To load all objects referenced in this file into the current R
## environment, make the following call at the R prompt:

knitr::opts_chunk$set(fig.width=7,
                      fig.height=7/(16/9),
                      dpi=200,
                      tinytex.verbose=TRUE, ## PDFs very slow to compile.
                      echo=FALSE,
                      include=FALSE,
                      results='asis',
                      cache=TRUE,
                      warning=FALSE)

## Also see knitr::opts_current$get() within a chunk to inspect then-active options.

options(tinytex.verbose=TRUE,
        tinytex.clean=FALSE)

```

```{r workhorse}

source("./ct-covid.R")

```

# Read This First

```{r readme, include=TRUE}

cat(paste0(readLines("readme.md", n=-1), collapse="\n"))

```

# Introduction to this Page

I started putting together graphs based on Connecticut Department of Public Health (DPH) data in late March, and I've been tweeting some of those graphs since the first week of April. If you're interested in what some of those earlier graphs looked like, you can find them on Twitter at 
[https://twitter.com/search?q=%23Connecticut%20%23covid19%20%40davidbraze&src=typed_query](https://twitter.com/search?q=%23Connecticut%20%23covid19%20%40davidbraze&src=typed_query). 

This page (the one you're looking at now) doesn't have all the graphs I've built. I expect to grow the collection, and add some narrative around the graphs, as time permits. Of course, I'll update the graphs as new data rolls in. Don't expect daily updates, but I guess I'll get around to it at least a couple of times a week. The date at the top of the page will always indicate when it was last updated.

Most of my time is spent with data focused on the topics of language, literacy, and education. My website, with occasional blog posts, can be found at [davebraze.org](https://davebraze.org/).

## Copyright & License

This page, and the graphs it contains, is copyright 2020 by me, David Braze. The page content and graphs are released under the [Creative Commons v4.0 CC-by license](https://creativecommons.org/licenses/by/4.0/). In short, you're free to re-use the graphs so long as you give clear attribution of their source.

# Show Me the Pictures

## Statewide Summary

```{r ct-stat-daily-change, include=TRUE, fig.height=7}

ct.stat.daily.change.plt

```

```{r usa-state-corona, include=TRUE}

usa.state.corona.plt

```


## Each Town

```{r town-rate, include=TRUE}

town.rate.plt

```

```{r town-by-county-rate, include=TRUE, fig.height=7}

town.by.county.rate.plt

```

```{r map-today, include=TRUE, fig.height=7}

map.today

```

# General Covid-19 Resources

## How Covid-19 Spreads, & How it Doesn't

Here is a nice blog post by Erin Bromage, PhD in microbiology and immunology, about how person to person transmission of Covid-19 actually works. It includes what specific information about what we know about what situations are more risky, and which ones are less risky: https://www.erinbromage.com/post/the-risks-know-them-avoid-them. 

I think this is a valuable article for people who are worried about how to manage their risk as governments start to scale back on Covid-19 restrictions on movement and business activities. 

## Plans for Re-opening

Staying home was always intended as a temporary measure. The point of it is to prevent the healthcare system from being overwhelmed and to allow time to build capacity for managing the spread of Covid-19 and treatment of those who become ill despite best efforts for containment. The question has always been how and when to reopen. It was never about whether or not to reopen at all.

Several credible "road maps" have been proposed for how re-open in a responsible way:

* American Enterprise Institute's plan is here: https://www.aei.org/research-products/report/national-coronavirus-response-a-road-map-to-reopening/
* Johns Hopkins University School of Public Health plan is here: https://www.centerforhealthsecurity.org/our-work/publications/public-health-principles-for-a-phased-reopening-during-covid-19-guidance-for-governors
* Duke University Center for Health Policy's plan is here: https://healthpolicy.duke.edu/sites/default/files/atoms/files/covid-19_surveillance_roadmap_final.pdf

```{r eval=FALSE}

## More info here: https://twitter.com/cmyeaton/status/1258512373750435842?s=20

``` 
